The Tracing package\\ \large a more in depth explanation

### 2015-05-19 manual/tex/models.tex
* minimal changes to the report/manual - -> updated information for tracers/logger/dynamic structured DEVS
Signed-off-by: Lttlemoi <lttlemoi+git@gmail.com>
changes during yesterday's meeting

When \textbf{sending messages} (\textbf{output function}), there are a few rules you should take into account. The message you want to send can only be a string. This string should be given to the port you want to send it through. The port will then create the actual messages (that are send over the models) and return them to you in a vector. All these messages (from possibly different ports) should be joined in 1 vector and be returned in the output function. The following functions will allow you to do so:
\begin{itemize}
	\item \textsl{t\_portptr Model::getPort(std::string name) const}
	\item \textsl{std::vector{\textless}n\_network::t\_msgptr{\textgreater} Port:: \\createMessages(std::string message)}
\end{itemize} 
Something like this would work: this-{\textgreater}getPort("OUT")-{\textgreater} \\createMessages("my\_message"); \\

@@

\section{Dynamic Structured DEVS}
Both atomic models and coupled models can implement the following function:
\begin{itemize}
	\item \textsl{bool Model::modelTransition(DSSharedState* shared);}
\end{itemize}
The \textsl{shared} parameter gives access to a shared state. This state can be used to organize structural changes from the bottom up. It will not be wiped in between transitions.\\
The return value indicates whether or not the simulator should look at the parent of the current model for performing Dynamic Structured DEVS. This way, not all models have to be consulted for structural changes.\\
In the \textsl{modelTransition} function, models can add and remove connections, ports and submodels. Currently, only adding and removing connections is supported.

>>>>

When \textbf{sending messages} (\textbf{output function}), there are a few rules you should take into account. The message you want to send can only be a string. This string should be given to the port you want to send it through. The port will then create the actual messages (that are send over the models) and return them to you in a vector. All these messages (from possibly different ports) should be joined in 1 vector and be returned in the output function. The following functions will allow you to do so:
\begin{itemize}
	\item \textsl{t\_portptr Model::getPort(std::string name) const}
	\item \textsl{std::vector{\textless}n\_network::t\_msgptr{\textgreater} Port:: \\createMessages(std::string message)}
\end{itemize} 
Something like this would work: \textsl{this-{\textgreater}getPort("OUT")-{\textgreater} \\createMessages("my\_message");} \\

@@

\section{Dynamic Structured DEVS}
Both atomic models and coupled models can implement the following function:
\begin{itemize}
	\item \textsl{bool Model::modelTransition(DSSharedState* shared);}
\end{itemize}
The \textsl{shared} parameter gives access to a shared state. This state can be used to organize structural changes from the bottom up. It will not be wiped in between transitions.\\
The return value indicates whether or not the simulator should look at the parent of the current model for performing Dynamic Structured DEVS. This way, not all models have to be consulted for structural changes.\\
In the \textsl{modelTransition} function, models can add and remove connections, ports and submodels. Do note that the same rules for creating objects still apply.
